---
title: "HW4"
output: html_document
---
```{r load-packages, include=FALSE}
library(dplyr)
library(magrittr)
library(knitr)
library(ggplot2)
library(mdsr)
library(resampledata)
library(tidyr)
library(gtools)
library(dplyr)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(mosaic)
require(mosaicData)
require(Defualt)
require(tidyquant)
```

#Building Predictive Models
```{r}
setwd("C:/Users/Melantha Shao/Desktop/UC/2021-2022/Fall 2021/BTMA 431/HW4")
load("btma.431.736.f2018.v2.rda")
Q1.df = data.frame(btma.431.736.f2018)
```
#1a
#Final Project Coefficient Estimate = 0.40
```{r}
fitQ1a <- lm(final.raw.score.excluding.bonus ~ ., data = Q1.df)
summary(fitQ1a)
```

#1b
```{r}
Q1b.df = data.frame(Q1.df$final.project, Q1.df$post.retake.midterm, (Q1.df$textbook.quiz.average)*(100/15),(Q1.df$HW.average)*(100/20), Q1.df$BANA, Q1.df$final.raw.score.excluding.bonus)
colnames(Q1b.df) <- c("final.project", "post.retake.midterm", "textbook.quiz.average", "HW.average", "BANA", "final.raw.score.excluding.bonus")
head(Q1b.df,5)
```
#Compared to the previous regression model, the followings changed
# [HW.average coefficient estimate]
# [HW.average standard error]
# [textbook.quiz.average coefficient estimate]
# [textbook.quiz.average standard error]
```{r}
fitQ1b <- lm(final.raw.score.excluding.bonus ~ ., data = Q1b.df)
summary(fitQ1b)
```
#1c
# The P-value = [0.36]

#1d
# The p-value to address whether post.retake.midterm score impacts the final score is different between BANA students and non-BANA students is [0.86]
```{r}
fitQ1d <- lm(final.raw.score.excluding.bonus ~ final.project + textbook.quiz.average + HW.average + post.retake.midterm + BANA + post.retake.midterm * BANA, data = Q1b.df)
summary(fitQ1d)
```
#1e
# The coefficient for log(final.project) = [0.38]
```{r}
fitQ1e <- lm(log(final.raw.score.excluding.bonus) ~ log(final.project) + log(textbook.quiz.average) + log(HW.average) + log(post.retake.midterm), data = Q1b.df)
summary(fitQ1e)
```
#Building Prescriptive Models
#2a
#Q(p) = 50 − 5p
# Optimal Price = [5.50], Optimal Profit = [101.25]
```{r}
P = seq(1, 9, by = 0.01)
D = 50 - 5*P
S = D *(P-1)
max(S)
P[which.max(S)]
```
# 2b
# Q(p) = 45 − 5p
# Optimal Price = [5.00], Optimal Profit = [80.00]
```{r}
P2 = seq(1, 9, by = 0.01)
D2 = 45 - 5*P2
S2 = D2 *(P2-1)
max(S2)
P2[which.max(S2)]
```
# Q(p) = 50 − 5p
# Optimal Price = [6.00], Optimal Profit = [125.00]
```{r}
P3 = seq(1, 9, by = 0.01)
D3 = 55 - 5*P3
S3 = D3 *(P3-1)
max(S3)
P3[which.max(S3)]
```
# 2c
# The shape of the curve is upward sloping
```{r}
M = seq(40, 60, by = 1)
OP = c()
for (i in 1:length(M)){
  P4 = seq(1, 15, by = 0.01)
  S4 = (M[i] - 5*P4) * (P4-1)
  OP[i] = P4[which.max(S4)]
}
Q2c.df = data.frame(M,OP)
ggplot()+ geom_line(data=Q2c.df,aes(y = OP,x = M),size=1)
```

# 2d
# The plot shows a downward sloping line
```{r}
M1 = 45
M2 = 55
k = seq(2, 8, by = 0.01)
OP45 = c()
OP55 = c()
for (i in 1:length(k)){
  P5 =  seq(1, 15, by = 0.01)
  S45 = (M1 - k[i]*P5) * (P5-1)
  S55 = (M2 - k[i]*P5) * (P5-1)
  OP45[i] = P5[which.max(S45)]
  OP55[i] = P5[which.max(S55)] 
}
Q2d.df = data.frame(k,OP45,OP55)
ggplot()+
  geom_line(data=Q2d.df,aes(y=OP45,x= k,colour="M = 45"),size=1 )+
  geom_line(data=Q2d.df,aes(y=OP55,x= k,colour="M = 55"),size=1) +
  scale_color_manual(name = "Y series", values = c("M = 45" = "red", "M = 55" = "blue")) +
  ylab("Optimal Price")
```
# When M = 45 and Optimal Price = 5, k = [5.00]
# When k = 5.00, M = 45, Optimal Price = [6.00]
```{r}
kval = filter(Q2d.df,OP45==5)
kval$k

OPval = filter(Q2d.df, k == kval$k)
OPval$OP55
```

#2e
# The optimal price = [3.90]


```{r}
Decision_Support_Tool <- function(dataset){
  df = data.frame(dataset)
  dataset$profit <- (df$price-1)*(df$quantity)
  Q2e.fit <- lm(profit ~ price + I(price^2), data=dataset)
  
  Price = seq(0, 15, by=0.01)
  Profit = c()
  intcpt <- summary(Q2e.fit)$coefficients[1,1] #Intercept
  pri <- summary(Q2e.fit)$coefficients[2,1]    #Coefficient for price
  pri_squ <- summary(Q2e.fit)$coefficients[3,1]#Coefficient for price^2
  
  for (i in 1:length(Price)){
    Profit[i] = intcpt + (pri * Price[i]) + (pri_squ *(Price[i]^2))#prediction of profit using intercept and coefficient extracted earlier
  }
  Profit
  predict.df = data.frame(Price,Profit)
  
  return (Price[which.max(Profit)])
}
```

# To use the function, load dataset first, and set dataset = file name
```{r}
load("salesData.rda")
Decision_Support_Tool(dataset = salesData)
```

























